Synthesizing Symmetric Lenses

### 2018-07-09 papers/SymmetricLenses/main.tex
fix build break

\subsection{\GreedySynth}
\label{subsec:greedy-synth}
The greedy algorithm is actually two greedy algorithms, one that greedily finds
symmetric DNF lenses (\GreedySynth) and one that greedily finds symmetric
sequence lenses (\GreedySeqSynth).
We describe this synthesis algorithm in the context of trying to find a lens
between \lstinline{"" | name.name*} and \lstinline{"" | name}, with the example
\lstinline{creater "John Doe" = "John"}.

@@

First, \PCF{CannotMap} checks if there could possibly be a lens satisfying the
examples. If there is not, \GreedySynth returns \None early. After this,
\GreedySynth finds the best lenses between each sequence pair of the left and
right DNF regular expressions, given the examples that match them. An internal
state for the algorithm is initialized from these. This state consists of two
things: an intermediate partial DNF Lens and a priority queue consisting of
potential sequence lenses.

@@

\begin{algorithm}
  \caption{\GreedySynth}
  \label{alg:greedysynth}
  \begin{algorithmic}[1]
    \Function{GreedySynth}{$\Examples,\DNFOf{(\Sequence_1,\Probability_1)\DNFSep\ldots\DNFSep(\Sequence_n,\Probability_n)},\DNFOf{(\SequenceAlt_1,\ProbabilityAlt_1)\DNFSep\ldots\DNFSep(\SequenceAlt_m,\ProbabilityAlt_m)}$}
    \If{$\Call{CannotMap}{\Examples,\DNFOf{(\Sequence_1,\Probability_1)\DNFSep\ldots\DNFSep(\Sequence_n,\Probability_n)},\DNFOf{(\SequenceAlt_1,\ProbabilityAlt_1)\DNFSep\ldots\DNFSep(\SequenceAlt_m,\ProbabilityAlt_m)}}$}
    \State $\ReturnVal{\None}$
    \EndIf
    \State $\SLS \gets
    \Call{\CartesianMap}{\GreedySeqSynth(\Examples),\ListOf{\Sequence_1;\ldots;\Sequence_n},\ListOf{\SequenceAlt_1;\ldots;\SequenceAlt_m}}$
    \State $\GreedyState \gets \Call{GreedyState.Init}{\SLS}$
    \While{$\Call{GreedyState.Continue}{\GreedyState}$}
    \State $(\GreedyState,\SSQLens) \gets
    \Call{GreedyState.PopBest}{\GreedyState}$
    \If{$\Call{GreedyState.UsefulAdd}{\GreedyState,\SSQLens}$}
    \State $\GreedyState \gets \Call{GreedyState.AddSeq}{\GreedyState,\SSQLens}$
    \EndIf
    \EndWhile
    \State \ReturnVal{\Call{GreedyState.ToDNFLens}{\GreedyState}}
    \EndFunction
  \end{algorithmic}
\end{algorithm}

@@

\begin{algorithm}
  \caption{\GreedySeqSynth}
  \label{alg:greedyseqsynth}
  \begin{algorithmic}[1]
    \Function{AtomSynth}{$\Examples,\PRegexStar{\DNFRegex}{\Probability},\PRegexStar{\DNFRegexAlt}{\ProbabilityAlt}$}
    \If{$\Call{CannotMap}{\Examples,\PRegexStar{\DNFRegex}{\Probability},\PRegexStar{\DNFRegexAlt}{\ProbabilityAlt}}$}
    \State $\ReturnVal{\None}$
    \Else
    \State $\ReturnVal{\Call{Map}{\PCF{Iterate},\GreedySynth(\Examples,\DNFRegex,\DNFRegexAlt)}}$
    \EndIf
    \EndFunction

>>>>

\subsection{\GreedySynth}
\label{subsec:greedy-synth}
The greedy algorithm is actually two greedy algorithms, one that greedily finds
symmetric DNF lenses (\GreedySynth) and one that greedily finds symmetric
sequence lenses (\GreedySeqSynth). We describe this synthesis algorithm in the
context of trying to find a lens between \lstinline{"" | name.name*} and
\lstinline{"" | name}.

@@

First, \PCF{CannotMap} checks if there could possibly be a lens satisfying the
examples. If there is not, \GreedySynth returns \None early. After this,
\GreedySynth finds the best lenses between each sequence pair of the left and
right DNF regular expressions, given the examples that match them. A priority
queue containing these sequence lenses is initialized from these
($\PCF{PQ.Create}$). The symmetric lens is built up iteratively from these
sequence lenses, the state of this partial lens is tracked in the lens builder,
$lb$.

@@

\begin{algorithm}
  \caption{\GreedySynth}
  \label{alg:greedysynth}
  \begin{algorithmic}[1]
    \Function{GreedySynth}{$\Examples,\DNFOf{(\Sequence_1,\Probability_1)\DNFSep\ldots\DNFSep(\Sequence_n,\Probability_n)},\DNFOf{(\SequenceAlt_1,\ProbabilityAlt_1)\DNFSep\ldots\DNFSep(\SequenceAlt_m,\ProbabilityAlt_m)}$}
    \If{$\Call{CannotMap}{\Examples,\DNFOf{(\Sequence_1,\Probability_1)\DNFSep\ldots\DNFSep(\Sequence_n,\Probability_n)},\DNFOf{(\SequenceAlt_1,\ProbabilityAlt_1)\DNFSep\ldots\DNFSep(\SequenceAlt_m,\ProbabilityAlt_m)}}$}
    \State $\ReturnVal{\None}$
    \EndIf
    \State $\SLS \gets
    \Call{\CartesianMap}{\GreedySeqSynth(\Examples),\ListOf{\Sequence_1;\ldots;\Sequence_n},\ListOf{\SequenceAlt_1;\ldots;\SequenceAlt_m}}$
    \State $\GreedyState \gets \Call{PQ.Create}{\SLS}$
    \State $lb \gets \Call{LensBuilder.Empty}{}$
    \While{$\Call{PQ.IsNonempty}{\GreedyState}$}
    \State $\SSQLens \gets
    \Call{PQ.PopBest}{\GreedyState}$
    \If{$\Call{LensBuilder.UsefulAdd}{lb,\SSQLens}$}
    \State $lb \gets \Call{GreedyState.AddSeq}{lb,\SSQLens}$
    \EndIf
    \EndWhile
    \State \ReturnVal{\Call{LensBuilder.ToDNFLens}{\GreedyState}}
    \EndFunction
  \end{algorithmic}
\end{algorithm}

@@

\begin{algorithm}
  \caption{\GreedySeqSynth}
  \label{alg:greedyseqsynth}
  \begin{algorithmic}[1]
    \Function{AtomSynth}{$\Examples,\PRegexStar{\DNFRegex}{\Probability},\PRegexStar{\DNFRegexAlt}{\ProbabilityAlt}$}
    \If{$\Call{CannotMap}{\Examples,\PRegexStar{\DNFRegex}{\Probability},\PRegexStar{\DNFRegexAlt}{\ProbabilityAlt}}$}
    \State $\ReturnVal{\None}$
    \Else
    \State $\ReturnVal{\IterateLensOf{\GreedySynth(\Examples,\DNFRegex,\DNFRegexAlt)}}$
    \EndIf
    \EndFunction
